### 2021-12-09 input/proposal.tex
todos

\begin{definition}[\label{def:forwarding}Forwarding]
  A \process $x$ \underline{f}orwards a message $m$ by
  \underline{s}ending it to its neighbors $y$ with metadata that
  depends on its local knowledge: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
\end{definition}

@@

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to eventually ($\eventually$) reach
consistent partitioning, each source $s$ must send
\texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
that are closer to it than any other source, along with enough
metadata to allow them to decide of their closest source. A simple
implementation based on Definition~\ref{def:scoped} consists in
ensuring that each \process $x$ eventually receives
$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
any source to it; the value $|\Pi_{sx}|$ being built over forwarding
along this path.

@@

Algorithm~\ref{algo:add} shows the few instructions that implement a
\emph{reactive} forwarding of best to reach consistent partitioning in
a static network where \processes never join, crash, nor leave the
system. As soon as a \process receives a better message, it delivers
and forwards it. The trade-off consists in decreasing termination time
at cost of increased traffic. For the sake of simplicity and to remove
obvious loops, a \process does not forward a notification to its
sender (Line~\ref{line:accumulator}). Figure~\ref{fig:add} illustrates
the behavior of this algorithm on a system comprising 4 \processes
$a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.  They \NAMEB
notifications $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
state with the lowest value $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, $b$ receives $\alpha_{d}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, $b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
exists. Ultimately, \processes discard last transiting
messages.
% Despite the obvious lack of traffic optimization,
The system reaches consistent partitioning.
\TODO{Traffic complexity here?}

@@

A naive attempt at implementing DCP resembles echoes in
acoustics. Following the principles of scoped broadcast as stated in
Definition~\ref{def:scoped}, staleness notifications propagate as long
as receivers' current partition is the targeted one, and when
staleness notifications reach the bordering \processes of the deleted
partition, it triggers a competition -- or an echo -- that goes
backward to fill the gap left open by removals.

@@

%% \NAME guarantees dynamic consistent partitioning by making extensive
%% use of \process-to-\process communications. It requires
%% \begin{inparaenum}[(i)]
%% \item purging stale control information, hence propagating $\delta$
%%   messages; and
%% \item retrieving the closest source, hence propagating $\alpha$
%%   messages.
%% \end{inparaenum}
\TODO{TODOUBLECHECK}. In terms of number of messages, in the average
case, a \process $i$ chosen uniformly at random among all \processes
creates a logical partition. Its messages $\alpha_i$ spread through
the network until reaching \processes that belong to another partition
closer to them. This splits partitions in half on average. Overall,
the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
\processes. This decreases every new partition until reaching one
\process per new partition: its source. The average number of messages
per \process is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor
      \log_2 a \rfloor}})$}, where \smash{$\overline{|O|}$} is the
average number of neighbors per \process.
% \TODO{Multiple receipt and
% multiple
%  delivery imply more messages (receipt bounded by $|O|$ as well).}
Deleting the $a^{th}$ partition generates twice as many messages as
creating the $a^{th}$ partition: $\delta$ messages travel through the
partition, then $\alpha$ messages compete to fill the gap.  Overall,
the communication complexity shows that \NAME scales well to the
number of partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.
%% \begin{algorithm}[h!]
%%   \input{input/algoedges.tex}
%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
%% \end{algorithm}

>>>>

\begin{definition}[\label{def:forwarding}Forwarding]
  A \process $x$ \underline{f}orwards a message $m$ by
  \underline{s}ending it to its neighbors $y$ with metadata that
  depends on its local knowledge: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \TODO{\oplus} \sigma_x)$.
\end{definition}

@@

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to eventually ($\eventually$) reach
consistent partitioning, each source $s$ must send
\texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
that are closer to it than any other source, along with enough
metadata to allow them to decide of their closest source. A simple
implementation based on Definition~\ref{def:scoped} consists in
ensuring that each \process $x$ eventually receives
$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
any source to it; the best value $|\Pi_{sx}|$ being built over
forwarding along this path.

@@

Algorithm~\ref{algo:add} shows the few instructions that implement a
\emph{reactive} forwarding of best to reach consistent partitioning in
a static network where \processes never join, crash, nor leave the
system. As soon as a \process receives a better message, it delivers
and forwards it. The trade-off consists in decreasing termination time
at cost of increased traffic. \TODO{For the sake of simplicity and to
  remove obvious loops, a \process does not forward a notification to
  its sender (Line~\ref{line:accumulator})}. Figure~\ref{fig:add}
illustrates the behavior of this algorithm on a system comprising 4
\processes $a$, $b$, $c$, and $d$. Both $a$ and $d$ become sources.
They \NAMEB notifications $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest value $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, $b$ receives
$\alpha_{d}^{1}$. Since it improves its own partition distance, it
keeps it and forwards it to its neighbors. In Figure~\ref{fig:addD},
$b$ discards $\alpha_{a}^{2}$, for it does not improve its partition
distance. Neither $c$ nor $d$ will ever acknowledge that Source~$a$
exists. Ultimately, \processes discard last transiting messages.
% Despite the obvious lack of traffic optimization,
The system reaches consistent partitioning.

\noindent \TODO{In terms of space complexity.} In terms of number of
messages, in the average case, a \process $x$ chosen uniformly at
random among all \processes creates a logical partition. Its messages
$\alpha_x$ spread through the network until reaching \processes that
belong to another partition closer to them. This splits partitions in
half on average. Overall, the $n^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 n \rfloor}})$}
\processes. This decreases every new partition until reaching one
\process per new partition: its source. The average number of messages
per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
number of neighbors per \process.

@@

A naive attempt at implementing DCP resembles echoes in
acoustics. Following the principles of scoped broadcast as stated in
Definition~\ref{def:scoped}, a \process that receives a staleness
notification forwards it only if the latter targets its current
partition. The staleness notifications propagate through the network
as long as they remain in the deleted partition. When they reach the
bordering \processes of the deleted partition, it triggers a
competition -- or an echo -- that goes backward to fill the gap left
open by removals. \TODO{as in FB.}

@@

%% \NAME guarantees dynamic consistent partitioning by making extensive
%% use of \process-to-\process communications. It requires
%% \begin{inparaenum}[(i)]
%% \item purging stale control information, hence propagating $\delta$
%%   messages; and
%% \item retrieving the closest source, hence propagating $\alpha$
%%   messages.
%% \end{inparaenum}
\TODO{TODOUBLECHECK}.
% \TODO{Multiple receipt and
% multiple
%  delivery imply more messages (receipt bounded by $|O|$ as well).}
Deleting the $a^{th}$ partition generates twice as many messages as
creating the $a^{th}$ partition: $\delta$ messages travel through the
partition, then $\alpha$ messages compete to fill the gap.  Overall,
the communication complexity shows that \NAME scales well to the
number of partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.
%% \begin{algorithm}[h!]
%%   \input{input/algoedges.tex}
%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
%% \end{algorithm}
